\setlength{\parindent}{10ex}


\section{How HPC and Parallel Computing Effect Our Lives}
Parallel Computing and HPC are effecting every single person on the planet.
If a person recognizes this or not does not change the fact. 
Graphic Processing Units use parallelism to improve CGI, Video Games, and Graphics capabilities.
HPC is used in Big Data processing to churn through countless bytes of data.
These computations produce several artifacts including but not limited to accurate Machine Learning models.
Models that may be able to predict global epidemics, crop yields, and weather patterns.

\par
On a smaller level, parallel computing facilitates our technological world. 
The servers that host the most prominent sites such as YouTube, Facebook, Google, Reddit, etc.
All of these servers use parallel computing to serve the billions of users on their platforms.
It is impossible for a single serial computer to handle this entire workload. 
Video Games improve year over year because of the parallel processing preformed by consumer GPU's.
These consumer GPU's improve annually to add new graphics techniques that improve video games.
However, this continual improvement is because of the inherent parallel architecture in a GPU.

\par
The improvements in graphics processing can not be understated in how it affects our lives.
It effects the movies we watch, the games we play, and even the buildings we inhabit.
Improved graphics processing allows for better Computer Aided Design (CAD).
This allows engineers to build more stable structures.
Better graphics processing allows studios to create realistic CGI movies, and amazing video games.
All of this is possible because of the parallel computing found in a graphics card.

\par
Deep Learning has changed the digital landscape. 
The idea being that more data into larger neural networks produce better models.
This idea has produced great strides in previously hard domains.
Speech recognition, natural language processing, and pattern recognition all benefit from deep learning.
Deep Learning is possible because of the advancements in the parallel architecture of GPUs.
Data Scientists use parallel graph algorithms to quickly compute large neural networks.
This has ushered in a new era of Machine Learning because of parallel computing.
This era has redefined the world in which we live.
These models are built so that companies can predict every aspect of our lives.
This gives an advantage for advertisers.

\par 
In conclusion, HPC and Parallel Computing is effecting our lives on a macro and micro scale. 
From the advertisements we see to the video games we play. 
This is because clustering computers still creates the most powerful machines.
Until quantum computing becomes a viable solution.
HPC and Parallel computing will continue to shape the world.
